Equivalence Testing and the Second Generation \emph{P}-Value

### 2019-04-24 manuscript.R2.Rmd
rounding a % based on simulations

The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to *r* = -0.99 and 0.99, with a true correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only `r prop*100`% of the correlations observed in the future will fall in this range.

>>>>

The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to *r* = -0.99 and 0.99, with a true correlation of 0.99) `r round(sgpv2,3)*100`% of the confidence interval overlaps with the equivalence range, even though in the long run only `r round(prop*100`)% of the correlations observed in the future will fall in this range.

### 2019-04-24 manuscript.R2.tex
rounding a % based on simulations

The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 35.29\% of the correlations observed in the future will fall in this range.

>>>>

The further away from 0, the larger the SGPV when the observed mean falls on the equivalence bound. The SGPV is the proportion of values in a 95\% confidence interval that overlap with the equivalence range, but not the probability that these values will be observed. In the most extreme case (i.e., a sample size of 4, and equivalence bounds set to \emph{r} = -0.99 and 0.99, with a true correlation of 0.99) 97.60\% of the confidence interval overlaps with the equivalence range, even though in the long run only 35.08\% of the correlations observed in the future will fall in this range.
